Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

```{r bookmedia1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, fig.show="hold", out.width="430px"}
for (catal in unique(df0$catalog)) {
  df2 <- subset(df0, catalog = catal)
  pagelimit = 50
  df2$document.type <- rep(NA, nrow(df2))
  df2$document.type[df2$pagecount > pagelimit] <- "book"
  df2$document.type[df2$pagecount <= pagelimit] <- "pamphlet"
  df2 <- df2[which(!is.na(df2$document.type)),]
  df2$document.type <- factor(df2$document.type)
  df2 <- df2 %>% group_by(publication_decade, document.type) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
  p <- ggplot(df2, aes(x = publication_decade, y = paper.consumption.km2, group = document.type))
  p <- p + geom_point(aes(shape = document.type), size = 5)
  p <- p + geom_smooth(method = "loess", color = "black")
  p <- p + ggtitle("Paper consumption per document type")
  p <- p + xlab("Year")
  p <- p + ylab("Paper consumption (km2)")
  p <- p + scale_color_manual(values=c("black", "darkgray"))
  # p <- p + guides(shape = "none") 
  p <- p + ggtitle(catal)
  print(p)
}
```

>>>>

```{r bookmedia1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, fig.show="hold", out.width="430px"}
for (catal in unique(df0$catalog)) {
  df2 <- subset(df0, catalog == catal)
  pagelimit = 50
  df2$document.type <- rep(NA, nrow(df2))
  df2$document.type[df2$pagecount > pagelimit] <- "book"
  df2$document.type[df2$pagecount <= pagelimit] <- "pamphlet"
  df2 <- df2[which(!is.na(df2$document.type)),]
  df2$document.type <- factor(df2$document.type)
  df2 <- df2 %>% group_by(publication_decade, document.type) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
  p <- ggplot(df2, aes(x = publication_decade, y = paper.consumption.km2, group = document.type))
  p <- p + geom_point(aes(shape = document.type), size = 5)
  p <- p + geom_smooth(method = "loess", color = "black")
  p <- p + ggtitle("Paper consumption per document type")
  p <- p + xlab("Year")
  p <- p + ylab("Paper consumption (km2)")
  p <- p + scale_color_manual(values=c("black", "darkgray"))
  # p <- p + guides(shape = "none") 
  p <- p + ggtitle(catal)
  print(p)
}
```
